Trump vs. Harris: A Data-Driven Forecast modeling the 2024 US Presidential Elections

### 2024-10-22 paper/paper.qmd
Update paper.qmd

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
library(tidyverse)
library(dplyr)
library(here)

cleaned_data <- read_csv(here::here("data/analysis_data/model_data.csv"))
lm_model <- readRDS(here::here("models/lm_model.rds"))

@@

library(tidyverse)
library(here)

cleaned_data <- read_csv(here::here("data/analysis_data/electoral_data.csv"))
lm_model_trump <- readRDS(here::here("models/lm_model_trump.rds"))
lm_model_harris <- readRDS(here::here("models/lm_model_harris.rds"))

@@

```{r}
#| label: fig-sum
#| fig-cap: [Need Edit]
#| fig-subcap: [""]
#| echo: false
#| eval: true
#| warning: false
#| message: false
cleaned_data <- read_csv(here::here("data/analysis_data/president_polls_cleaned.csv"))

>>>>

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
library(tidyverse)
library(dplyr)
library(here)
library(arrow)

cleaned_data <- read_parquet(here::here("data/analysis_data/model_data.parquet"))
lm_model <- readRDS(here::here("models/lm_model.rds"))

@@

library(tidyverse)
library(here)
library(arrow)

cleaned_data <- read_parquet(here::here("data/analysis_data/electoral_data.parquet"))
lm_model_trump <- readRDS(here::here("models/lm_model_trump.rds"))
lm_model_harris <- readRDS(here::here("models/lm_model_harris.rds"))

@@

```{r}
#| label: fig-sum
#| fig-cap: [Need Edit]
#| fig-subcap: [""]
#| echo: false
#| eval: true
#| warning: false
#| message: false
cleaned_data <- read_parquet(here::here("data/analysis_data/president_polls_cleaned.parquet"))
